Applied Temporal Analysis: A Complete Run of the FraCaS Test Suite

### 2021-02-09 paper2020/paper.tex
merge changes

\title{FraCaS: Temporal Analysis}
% \author{\ifanon Anonymous for review\else
%   \authorname{Jean-Philippe Bernardy} \authorname{Stergios Chatzikyriakidis}
%   \affiliation{University of Gothenburg}
%   \email{firstname.lastname@gu.se}\fi}

@@

\begin{abstract}
In this paper, we propose an implementation of temporal semantics
  which is suitable for inference problems. This implementation
  translates syntax trees to logical formulas, suitable for
  consumption by the Coq proof assistant. We support several phenomena
  including: temporal references, temporal adverbs, aspectual classes
  and progressives.  We apply these semantics to the complete FraCaS testsuite.
  We obtain an accuracy of 81 percent overall and 73 percent for problems explicitly marked
  as related to temporal reference.
\end{abstract}

@@

Unicity of action holds only if the aspectual class of the proposition
$P$ is \emph{activity}~\citep{steedman_productions_2000} (which, for our
purposes, includes \emph{achievements} and \emph{accomplishments}).

@@

\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}[hbt]
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#FraCaS
                          & This        & FC2         & FC & MINE & Nut  & LP  \\ \hline
Quantifiers  & 75         & .93        & .96         & .96    & .77  & .53  & .93  \\
             &            & \ncases{74}& \ncases{74} &        &      &      &     \ncases{44} \\
Plurals      & 33         & .79        & .82         & .76    & .67  & .52  & .73 \\
             &            &            &             &     &   &   & \ncases{24} \\
Anaphora     & 28         & .79        & .86         &   -    & -    & -    &  -       \\
Ellipsis     & 52         & .81        & .87         &   -    & -    & -    &  -       \\
Adjectives   & 22         & .95        & .95         & .95    & .68  & .32  & .73 \\
             &            & \ncases{20}&  \ncases{20}&     &   &   &  \ncases{12} \\
Comparatives & 31         & .65        & .87         & .56    & .48  & .45  &  -       \\
Temporal     & 75         & .73        &  -          &   -    &   -  &  -   &  -       \\
Verbs        & 8          & .75        & .75         &   -    & -    & -    &  -       \\
Attitudes    & 13         & .85        & .92         & .85    & .77  & .46  & .92  \\ 
             &            &            &             &        &      &      & \ncases {9}  \\ \hline
Total        & 337        & .81        & .89         & .83    & .69  & .50  & .85  \\
             &            & \ncases{329}& \ncases{259}& \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Accuracy of our system compared to others.
    ``This" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the second column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FC''
    refers to the work of \citet{bernardy_type-theoretical_2017}, and ``FC2'' its followup~\citep{bernardy_wide-coverage_2019}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilises the first-order automated theorem prover
    \textit{nutcracker} \cite{bos:2008}, and ``Langpro"
    to the system presented by \citet{abzianidze_tableau_2015}. A dash
    indicates that no attempt was made for the section. }
  \label{tab:results}
\end{table}
Additionally, to provide the reader with a better sense of what the
complete system is capable and not capable of, we list a number of
correctly and incorrectly handled examples in \cref{fig:correct-examples} and \cref{fig:incorrect-examples}.
\paragraph{Interaction with anaphora}
\label{sec:interaction-with-anaphora}
One reason explaining the lower performance of our system on some
sections of the testsuite is that our interpretation of time interacts
imperfectly with anaphora and ellipsis. Consider the following example:

@@

\cite{bernardy_wide-coverage_2019} presented a
logical system for handling 8 of the 9 sections of the FRACAS test
suite, but excluded section 7, suggesting that it requires many
examples that need an \textit{ad hoc} treatment. Here, we take up this
challenge and show that a system similar to theirs can be extended to
cover the remaining section of the test suite.
%
We use the same combination of a number of well-studied tools: type
theory, parsing using the Grammatical Framework (GF), Monadic Dynamic
Semantics and proof assistant technology (Coq). The system achieves an
accuracy of 0.73 on the Temporal Section and 0.81 overall.
One of the
things to be looked at is fixing the issues associated with parts of
the test suite that ``broke'' when the temporal analysis was
introduced. Some of these have been already mentioned: interaction of
the temporal variables with anaphora.

>>>>

\title{Applied Temporal Analysis: A Complete Run of the FraCaS Test Suite }
% \author{\ifanon Anonymous for review\else
%   \authorname{Jean-Philippe Bernardy} \authorname{Stergios Chatzikyriakidis}
%   \affiliation{University of Gothenburg}
%   \email{firstname.lastname@gu.se}\fi}

@@

\begin{abstract}In this paper, we propose an implementation of temporal semantics that
  translates syntax trees to logical formulas, suitable for
 consumption by the Coq proof assistant. The analysis  supports a wide range of phenomena
 including: temporal references, temporal adverbs, aspectual classes
 and progressives.  The new semantics are built on top of a previous system handling all sections of the FraCaS test suite except the temporal reference section, and we  obtain an accuracy of 81 percent overall and 73 percent for the problems explicitly marked
as related to temporal reference. To the best of our knowledge, this is the best performance of a logical system on the whole of the FraCaS. 
\end{abstract}

@@

Unicity of action holds only if the aspectual class of the proposition
$P$ is \emph{activity}~\citep{steedman_productions_2000} (which, for our
purposes, includes \emph{achievements} and \emph{accomplishments} as well).

@@

\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}[hbt]
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#FraCaS
                          & This        & FC2         & FC & MINE & Nut  & LP  \\ \hline
Quantifiers  & 75         & .93        & .96         & .96    & .77  & .53  & .93  \\
             &            & \ncases{74}& \ncases{74} &        &      &      &     \ncases{44} \\
Plurals      & 33         & .79        & .82         & .76    & .67  & .52  & .73 \\
             &            &            &             &     &   &   & \ncases{24} \\
Anaphora     & 28         & .79        & .86         &   -    & -    & -    &  -       \\
Ellipsis     & 52         & .81        & .87         &   -    & -    & -    &  -       \\
Adjectives   & 22         & .95        & .95         & .95    & .68  & .32  & .73 \\
             &            & \ncases{20}&  \ncases{20}&     &   &   &  \ncases{12} \\
Comparatives & 31         & .65        & .87         & .56    & .48  & .45  &  -       \\
Temporal     & 75         & .73        &  -          &   -    &   -  &  -   &  -       \\
Verbs        & 8          & .75        & .75         &   -    & -    & -    &  -       \\
Attitudes    & 13         & .85        & .92         & .85    & .77  & .46  & .92  \\ 
             &            &            &             &        &      &      & \ncases {9}  \\ \hline
Total        & 337        & .81        & .89         & .83    & .69  & .50  & .85  \\
             &            & \ncases{329}& \ncases{259}& \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Accuracy of our system compared to others.
    ``This" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the second column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FC''
    refers to the work of \citet{bernardy_type-theoretical_2017}, and ``FC2'' its followup~\citep{bernardy_wide-coverage_2019}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilises the first-order automated theorem prover
    \textit{nutcracker} \cite{bos:2008}, and ``Langpro"
    to the system presented by \citet{abzianidze_tableau_2015}. A dash
    indicates that no attempt was made for the section. }
  \label{tab:results}
\end{table}
%Additionally, to provide the reader with a better sense of what the
%complete system is capable and not capable of, we list a number of
%correctly and incorrectly handled examples in \cref{fig:correct-examples} and \cref{fig:incorrect-examples}.
\paragraph{Interaction with anaphora}
\label{sec:interaction-with-anaphora}
One reason explaining the lower performance of our system on some
sections of the testsuite is that our interpretation of time interacts
imperfectly with anaphora and ellipsis. Consider the following example:

@@

\cite{bernardy_wide-coverage_2019} presented a
logical system for handling 8 of the 9 sections of the FraCaS test
suite, but excluded section 7, suggesting that it requires many
examples that need an \textit{ad hoc} treatment. Here, we took up this
challenge and have shown that a system similar to theirs can be extended to
cover the remaining section of the test suite, without considerably decreasing the performance of the 
rest of the sections. This is indeed a common problem with logical approaches, namely the fact that one can have theoretically motivated implementations of individual phenomena, e.g. anaphora, ellipsis, quantifiers, temporal reference etc., but when one tries to put all these together into a unified system, this proves to be a daunting task. We believe that this paper presents an exception, and provides a system that can deal with all these different semantic phenomena under a unified system with very good results. 
%
We use the same combination of a number of well-studied tools: type
theory, parsing using the Grammatical Framework (GF), Monadic Dynamic
Semantics and proof assistant technology (Coq). The system achieves an
accuracy of 0.73 on the Temporal Section and 0.81 overall.
One of the
things to be looked at is fixing the issues associated with parts of
the test suite that ``broke'' when the temporal analysis was
introduced. Some of these have been already mentioned: interaction of
the temporal variables with anaphora.
